Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-04 Latex Source/paper.tex
finished design

\AtBeginDocument{%
  \providecommand\BibTeX{{%  
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}} %chktex 1

\usepackage{etoolbox} 
\apptocmd{\sloppy}{\hbadness 10000\relax} {}{} %chktex 1

\usepackage[skip=6pt plus1pt]{parskip} %% add space between the paragraphs

\usepackage{graphicx} %% For pictures
\graphicspath{{./pics/}}
\usepackage[section]{placeins} %% used to keep the images in the section that I want them in

\setcopyright{acmcopyright}
\copyrightyear{2024}
\acmYear{2024}
\acmDOI{XXXXXXX.XXXXXXX}

@@

\ccsdesc{Music, Typing Efficiency} % Update this
\keywords{Typing Efficiency with Music, Cognitive Function} % placeholder text for the time being
\maketitle

@@

\subsection{Eye Tracking and Quantified Behavioral Test}
Citations about eye tracking and QBTest here

\section{Methodology}
After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
The interface automatically calculated typing accuracy and the time the attempt took in the program's backend, allowing participants to focus solely on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
The GUI of the typing test was built with simplicity in mind. The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1. The participants saw Figure 2 while the test is running, while Figure 3 is the signifier that the typing portion is finished.

@@

Participants were seated in a comfortable position facing the laptop screen.
The laptop is placed on top of a laptop stand while the eye tracker is mounted on a wooden frame. 
While the eye tracker is on a moveable slider, it is centered in front of the screen. 
At the ends of the wooden frame are infrared lights that flashes at sixty frames per second. % will need to verify that it is 60 fps.
Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QBTest).

@@

% Further details on the cognitive task will be provided in subsequent sections. They will then move on the the QBTest?. % This will need to be re-written.

\subsection[short]{Equipment} 
% This may not need to be broken into subsections. Will decide before we resubmit. 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QBTest.

QBTest MacBook Pro with Eye Tracker: This MacBook Pro was dedicated to conducting the QBTest. It had the eye tracker mounted on it, which made it difficult to access the keyboard for typing. Participants used this MacBook Pro for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test. A bluetooth keyboard was used as part of the QBTest since the positioning of the Eye Writer mostly blocked the space bar.

Typing Test MacBook Pro: The second MacBook Pro was used for the typing test. Since it did not have the eye tracker mounted on it, participants could easily access the keyboard and perform the typing test without any interference from the eye tracker.
Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.

\subsection[short]{Procedure}
Each participant was instructed to read and then sign the consent form. While the consent form had the basis of what they would be doing, they were given more detail as to the instructions when they were ready to begin.
 %REWRITE THIS HERE
%First they would take the short typing test three times to account for the three levels of music. 
%They would then do a QBTest three times again for the music. 
%The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
The two computers were set up side by side so that it would be easy for the participant to switch between the typing test and QBTest.
This setup also made it simple for the music component as the participants did each level together 
(e.g. typing test then QBTest without having to change the music or swapping to no music)
before moving on to the next level. 
Because of the way that the heatmap was coded, we had to make sure that each level was done in the same order for all the participants.
We made sure to always do instrumental music, lyrical music, then no music.

\subsection[short]{Participants and Design}
Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. Two males and eight females all in the age range of 18-23. There were no restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
They have all previously either learned to type at primary school or through necessity.

>>>>

% part of the template 
\AtBeginDocument{%
  \providecommand\BibTeX{{%  
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}} %chktex 1

% part of the template 
\setcopyright{acmcopyright}
\copyrightyear{2024}
\acmYear{2024}
\acmDOI{XXXXXXX.XXXXXXX}

% packages that I added
\usepackage{graphicx} %% For pictures
\graphicspath{{./pics/}}
\usepackage[section]{placeins} %% used to keep the images in the section that I want them in

@@

\ccsdesc{Music, Typing Efficiency, Cognitive Function}
\keywords{Typing Efficiency with Music, Cognitive Function, Quantified Behavioral Test}
\maketitle

@@

\subsection{Eye Tracking and Quantified Behavioral Test}

CITATIONS ABOUT EYE TRACKING AND QBTEST HERE

\section{Methodology}
\subsection[short]{Equipment} 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test and QBTest. 
Participants used the MacBook Pro with the eye tracker for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test. 
A bluetooth keyboard allowed participants to press the space bar in the Quantified Behavioral test easily as the mounting of the eye tracker made it harder to access
the space bar on the MacBook.
Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.

\subsection[short]{Procedure}
Each participant was instructed to read and then sign the consent form. While the consent form had the basis of what they would be doing, they were given more detail as to the instructions when they were ready to begin.
The two computers were set up side by side so that it would be easy for the participant to switch between the typing test and QBTest.
This setup also made it simple for the music component as the participants did each level together 
(e.g. typing test then QBTest without having to change the music or swapping to no music)
before moving on to the next level. 
Because of the way that the heatmap was coded, we had to make sure that each level was done in the same order for all the participants.
We made sure to always do instrumental music, lyrical music, then no music.

\subsection[short]{Participants}
Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. Two males and eight females all in the age range of 18-23. There were no restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
They have all previously either learned to type at primary school or through necessity.

\subsection[short]{Design}
After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
The interface automatically calculated typing accuracy and the time the attempt took in the program's backend, allowing participants to focus solely on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
The GUI of the typing test was built with simplicity in mind. The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1. The participants saw Figure 2 while the test is running, while Figure 3 is the signifier that the typing portion is finished.

@@

Participants were seated in a comfortable position facing the laptop screen.
The laptop is placed on top of a laptop stand while the eye tracker is mounted on a wooden frame. 
While the eye tracker is on a moveable slider, it is centered in front of the screen. 
At the ends of the wooden frame are infrared lights that flashes at sixty frames per second. % WILL NEED TO VERIFY THAT IT IS 60 FPS
Although not pictured, a bluetooth keyboard is used by the participant for the quantified behavioral test (QBTest).

@@
